---
title: "Lab Exercise 2"
author: "Charles Daniel Songaling"
date: "2024-02-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)
```

#Product 1 
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset1 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset1)
}

link1 <- "https://www.amazon.com.au/BENGOO-G9000-Stereo-Gaming-Headset/product-reviews/B01H6GUCCQ/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/BENGOO-G9000-Stereo-Gaming-Headset/product-reviews/B01H6GUCCQ/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/BENGOO-G9000-Stereo-Gaming-Headset/product-reviews/B01H6GUCCQ/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/BENGOO-G9000-Stereo-Gaming-Headset/product-reviews/B01H6GUCCQ/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/BENGOO-G9000-Stereo-Gaming-Headset/product-reviews/B01H6GUCCQ/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)
product_review1 <- rbind(pg1, pg2, pg3, pg4, pg5)
#View(product_review1)

```


#Product 2
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset2 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset2)
}

link1 <- "https://www.amazon.com.au/HyperX-KHX-HSCP-GM-Headset-Virtual-Surround/product-reviews/B00SAYCVTQ/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/HyperX-KHX-HSCP-GM-Headset-Virtual-Surround/product-reviews/B00SAYCVTQ/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/HyperX-KHX-HSCP-GM-Headset-Virtual-Surround/product-reviews/B00SAYCVTQ/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/HyperX-KHX-HSCP-GM-Headset-Virtual-Surround/product-reviews/B00SAYCVTQ/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/HyperX-KHX-HSCP-GM-Headset-Virtual-Surround/product-reviews/B00SAYCVTQ/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)
product_review2 <- rbind(pg1, pg2, pg3, pg4, pg5)
#View(product_review2)

```


#Product 3
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  amazonheadset3 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset3)
}

link1 <- "https://www.amazon.com.au/Jabra-Evolve-Headset-Smartphone-softphone/product-reviews/B00ODRSGX4/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Jabra-Evolve-Headset-Smartphone-softphone/product-reviews/B00ODRSGX4/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Jabra-Evolve-Headset-Smartphone-softphone/product-reviews/B00ODRSGX4/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Jabra-Evolve-Headset-Smartphone-softphone/product-reviews/B00ODRSGX4/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Jabra-Evolve-Headset-Smartphone-softphone/product-reviews/B00ODRSGX4/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)
product_review3 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review3)

```


#Product 4
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset4 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset4)
}

link1 <- "https://www.amazon.com.au/Razer-Barracuda-Wireless-Multi-Platform-Headset/product-reviews/B09BD6DKL5/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Razer-Barracuda-Wireless-Multi-Platform-Headset/product-reviews/B09BD6DKL5/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Razer-Barracuda-Wireless-Multi-Platform-Headset/product-reviews/B09BD6DKL5/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Razer-Barracuda-Wireless-Multi-Platform-Headset/product-reviews/B09BD6DKL5/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Razer-Barracuda-Wireless-Multi-Platform-Headset/product-reviews/B09BD6DKL5/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)
product_review4 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review4)

```


#Product 5
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset5 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset5)
}

link1 <- "https://www.amazon.com.au/SteelSeries-Arctis-Nova-Multi-Platform-PlayStation/product-reviews/B0B7X8D45M/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/SteelSeries-Arctis-Nova-Multi-Platform-PlayStation/product-reviews/B0B7X8D45M/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/SteelSeries-Arctis-Nova-Multi-Platform-PlayStation/product-reviews/B0B7X8D45M/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/SteelSeries-Arctis-Nova-Multi-Platform-PlayStation/product-reviews/B0B7X8D45M/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/SteelSeries-Arctis-Nova-Multi-Platform-PlayStation/product-reviews/B0B7X8D45M/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)
product_review5 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review5)

```


#Product 6
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset6 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset6)
}

link1 <- "https://www.amazon.com.au/SteelSeries-Arctis-Nova-Illumination-Playstation/product-reviews/B0B7X65SX2/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/SteelSeries-Arctis-Nova-Illumination-Playstation/product-reviews/B0B7X65SX2/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/SteelSeries-Arctis-Nova-Illumination-Playstation/product-reviews/B0B7X65SX2/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/SteelSeries-Arctis-Nova-Illumination-Playstation/product-reviews/B0B7X65SX2/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/SteelSeries-Arctis-Nova-Illumination-Playstation/product-reviews/B0B7X65SX2/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)
product_review6 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review6)

```


#Product 7
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset7 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset7)
}

link1 <- "https://www.amazon.com.au/Razer-BlackShark-V2-Gaming-Headset/product-reviews/B086PKMZ21/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Razer-BlackShark-V2-Gaming-Headset/product-reviews/B086PKMZ21/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Razer-BlackShark-V2-Gaming-Headset/product-reviews/B086PKMZ21/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Razer-BlackShark-V2-Gaming-Headset/product-reviews/B086PKMZ21/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Razer-BlackShark-V2-Gaming-Headset/product-reviews/B086PKMZ21/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)
product_review7 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review7)

```


#Product 8
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset8 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset8)
}

link1 <- "https://www.amazon.com.au/Jabra-Evolve2-Wireless-Headset-USB/product-reviews/B086KBXB3G/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Jabra-Evolve2-Wireless-Headset-USB/product-reviews/B086KBXB3G/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Jabra-Evolve2-Wireless-Headset-USB/product-reviews/B086KBXB3G/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Jabra-Evolve2-Wireless-Headset-USB/product-reviews/B086KBXB3G/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Jabra-Evolve2-Wireless-Headset-USB/product-reviews/B086KBXB3G/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)
product_review8 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review8)

```


#Product 9
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset9 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset9)
}

link1 <- "https://www.amazon.com.au/Plantronics-Bluetooth-Single-Ear-USB-Compatible/product-reviews/B07DFQWGYB/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Plantronics-Bluetooth-Single-Ear-USB-Compatible/product-reviews/B07DFQWGYB/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Plantronics-Bluetooth-Single-Ear-USB-Compatible/product-reviews/B07DFQWGYB/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Plantronics-Bluetooth-Single-Ear-USB-Compatible/product-reviews/B07DFQWGYB/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Plantronics-Bluetooth-Single-Ear-USB-Compatible/product-reviews/B07DFQWGYB/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)
product_review9 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review9)

```


#Product 10
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset10 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset10)
}

link1 <- "https://www.amazon.com.au/EPOS-Professional-Gaming-Lightweight-Comfortable/product-reviews/B09FPD2TP1/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/EPOS-Professional-Gaming-Lightweight-Comfortable/product-reviews/B09FPD2TP1/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/EPOS-Professional-Gaming-Lightweight-Comfortable/product-reviews/B09FPD2TP1/ref=cm_cr_arp_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/EPOS-Professional-Gaming-Lightweight-Comfortable/product-reviews/B09FPD2TP1/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/EPOS-Professional-Gaming-Lightweight-Comfortable/product-reviews/B09FPD2TP1/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)
product_review10 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review10)

```


#Product 11
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset11 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset11)
}

link1 <- "https://www.amazon.com.au/Corsair-Wireless-Customisable-Aluminium-Compatibility/product-reviews/B07Y2MBBT9/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Corsair-Wireless-Customisable-Aluminium-Compatibility/product-reviews/B07Y2MBBT9/ref=cm_cr_getr_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Corsair-Wireless-Customisable-Aluminium-Compatibility/product-reviews/B07Y2MBBT9/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Corsair-Wireless-Customisable-Aluminium-Compatibility/product-reviews/B07Y2MBBT9/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Corsair-Wireless-Customisable-Aluminium-Compatibility/product-reviews/B07Y2MBBT9/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)
product_review11 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review11)

```


#Product 12
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset12 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset12)
}

link1 <- "https://www.amazon.com.au/Turtle-Beach-Playstation-Nintendo-Connection/product-reviews/B08486NP2G/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Turtle-Beach-Playstation-Nintendo-Connection/product-reviews/B08486NP2G/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Turtle-Beach-Playstation-Nintendo-Connection/product-reviews/B08486NP2G/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Turtle-Beach-Playstation-Nintendo-Connection/product-reviews/B08486NP2G/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Turtle-Beach-Playstation-Nintendo-Connection/product-reviews/B08486NP2G/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)
product_review12 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review12)

```


#Product 13
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset13 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset13)
}

link1 <- "https://www.amazon.com.au/EPOS-Detachable-Audio-Playstation-Compatible/product-reviews/B099KPHR5B/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/EPOS-Detachable-Audio-Playstation-Compatible/product-reviews/B099KPHR5B/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/EPOS-Detachable-Audio-Playstation-Compatible/product-reviews/B099KPHR5B/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/EPOS-Detachable-Audio-Playstation-Compatible/product-reviews/B099KPHR5B/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/EPOS-Detachable-Audio-Playstation-Compatible/product-reviews/B099KPHR5B/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)
product_review13 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review13)

```


#Product 14
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset14 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset14)
}

link1 <- "https://www.amazon.com.au/Jabra-Evolve-20-UC-Stereo/product-reviews/B00ODRSBPW/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Jabra-Evolve-20-UC-Stereo/product-reviews/B00ODRSBPW/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Jabra-Evolve-20-UC-Stereo/product-reviews/B00ODRSBPW/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Jabra-Evolve-20-UC-Stereo/product-reviews/B00ODRSBPW/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Jabra-Evolve-20-UC-Stereo/product-reviews/B00ODRSBPW/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)
product_review14 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review14)

```


#Product 15
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset15 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset15)
}

link1 <- "https://www.amazon.com.au/Jabra-Evolve-Wireless-Stereo-Headset/product-reviews/B09Z2RTQHC/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Jabra-Evolve-Wireless-Stereo-Headset/product-reviews/B09Z2RTQHC/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Jabra-Evolve-Wireless-Stereo-Headset/product-reviews/B09Z2RTQHC/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Jabra-Evolve-Wireless-Stereo-Headset/product-reviews/B09Z2RTQHC/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Jabra-Evolve-Wireless-Stereo-Headset/product-reviews/B09Z2RTQHC/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)
product_review15 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review15)

```


#Product 16
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset16 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset16)
}

link1 <- "https://www.amazon.com.au/Razer-BlackShark-V2-Special-Edition/product-reviews/B091FBWFYF/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Razer-BlackShark-V2-Special-Edition/product-reviews/B091FBWFYF/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Razer-BlackShark-V2-Special-Edition/product-reviews/B091FBWFYF/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Razer-BlackShark-V2-Special-Edition/product-reviews/B091FBWFYF/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Razer-BlackShark-V2-Special-Edition/product-reviews/B091FBWFYF/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)
product_review16 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review16)

```


#Product 17
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset17 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset17)
}

link1 <- "https://www.amazon.com.au/Voyager-Wireless-Headset-Charging-Plantronics/product-reviews/B09VYGY8R6/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Voyager-Wireless-Headset-Charging-Plantronics/product-reviews/B09VYGY8R6/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Voyager-Wireless-Headset-Charging-Plantronics/product-reviews/B09VYGY8R6/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Voyager-Wireless-Headset-Charging-Plantronics/product-reviews/B09VYGY8R6/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Voyager-Wireless-Headset-Charging-Plantronics/product-reviews/B09VYGY8R6/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review17 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review17)

```


#Product 18
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset18 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset18)
}

link1 <- "https://www.amazon.com.au/Razer-Kraken-HyperSense-Headset-Technology/product-reviews/B09D45HQ8N/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Razer-Kraken-HyperSense-Headset-Technology/product-reviews/B09D45HQ8N/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Razer-Kraken-HyperSense-Headset-Technology/product-reviews/B09D45HQ8N/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Razer-Kraken-HyperSense-Headset-Technology/product-reviews/B09D45HQ8N/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Razer-Kraken-HyperSense-Headset-Technology/product-reviews/B09D45HQ8N/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review18 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review18)

```


#Product 19
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset19 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset19)
}

link1 <- "https://www.amazon.com.au/Turtle-Beach-Force-Recon-Black/product-reviews/B00YXO5UKY/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Turtle-Beach-Force-Recon-Black/product-reviews/B00YXO5UKY/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Turtle-Beach-Force-Recon-Black/product-reviews/B00YXO5UKY/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Turtle-Beach-Force-Recon-Black/product-reviews/B00YXO5UKY/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Turtle-Beach-Force-Recon-Black/product-reviews/B00YXO5UKY/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review19 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review19)

```


#Product 20
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset20 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset20)
}

link1 <- "https://www.amazon.com.au/Plantronics-VOYAGER5200NEW-Voyager-5200-Headset/product-reviews/B079DDRSNM/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Plantronics-VOYAGER5200NEW-Voyager-5200-Headset/product-reviews/B079DDRSNM/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Plantronics-VOYAGER5200NEW-Voyager-5200-Headset/product-reviews/B079DDRSNM/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Plantronics-VOYAGER5200NEW-Voyager-5200-Headset/product-reviews/B079DDRSNM/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Plantronics-VOYAGER5200NEW-Voyager-5200-Headset/product-reviews/B079DDRSNM/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review20 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review20)

```


#Product 21
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset21 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset21)
}

link1 <- "https://www.amazon.com.au/Razer-AU-Kraken-Headset-RZ04-02980200-R3M1/product-reviews/B07WLWNPZJ/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Razer-AU-Kraken-Headset-RZ04-02980200-R3M1/product-reviews/B07WLWNPZJ/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Razer-AU-Kraken-Headset-RZ04-02980200-R3M1/product-reviews/B07WLWNPZJ/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Razer-AU-Kraken-Headset-RZ04-02980200-R3M1/product-reviews/B07WLWNPZJ/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Razer-AU-Kraken-Headset-RZ04-02980200-R3M1/product-reviews/B07WLWNPZJ/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review21 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review21)

```


#Product 22
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset22 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset22)
}

link1 <- "https://www.amazon.com.au/Pulse-3D-Wireless-Headset-PlayStation/product-reviews/B08H99878P/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Pulse-3D-Wireless-Headset-PlayStation/product-reviews/B08H99878P/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Pulse-3D-Wireless-Headset-PlayStation/product-reviews/B08H99878P/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Pulse-3D-Wireless-Headset-PlayStation/product-reviews/B08H99878P/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Pulse-3D-Wireless-Headset-PlayStation/product-reviews/B08H99878P/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review22 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review22)

```


#Product 23
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset23 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset23)
}

link1 <- "https://www.amazon.com.au/EPOS-Open-Professional-Gaming-Lightweight/product-reviews/B09FPFN78X/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/EPOS-Open-Professional-Gaming-Lightweight/product-reviews/B09FPFN78X/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/EPOS-Open-Professional-Gaming-Lightweight/product-reviews/B09FPFN78X/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/EPOS-Open-Professional-Gaming-Lightweight/product-reviews/B09FPFN78X/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/EPOS-Open-Professional-Gaming-Lightweight/product-reviews/B09FPFN78X/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review23 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review23)

```


#Product 24
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset24 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset24)
}

link1 <- "https://www.amazon.com.au/Turtle-Beach-Headset-Recon-70P/product-reviews/B07NQX1J99/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Turtle-Beach-Headset-Recon-70P/product-reviews/B07NQX1J99/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Turtle-Beach-Headset-Recon-70P/product-reviews/B07NQX1J99/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Turtle-Beach-Headset-Recon-70P/product-reviews/B07NQX1J99/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Turtle-Beach-Headset-Recon-70P/product-reviews/B07NQX1J99/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review24 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review24)

```


#Product 25
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset25 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset25)
}

link1 <- "https://www.amazon.com.au/Plantronics-Blackwire-Cancelling-Soundguard-Microphone/product-reviews/B089QVZBWM/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Plantronics-Blackwire-Cancelling-Soundguard-Microphone/product-reviews/B089QVZBWM/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Plantronics-Blackwire-Cancelling-Soundguard-Microphone/product-reviews/B089QVZBWM/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Plantronics-Blackwire-Cancelling-Soundguard-Microphone/product-reviews/B089QVZBWM/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Plantronics-Blackwire-Cancelling-Soundguard-Microphone/product-reviews/B089QVZBWM/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review25 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review25)

```


#Product 26
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset26 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset26)
}

link1 <- "https://www.amazon.com.au/Jabra-Evolve2-Headset-Cancelling-USB/product-reviews/B086H56JDY/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Jabra-Evolve2-Headset-Cancelling-USB/product-reviews/B086H56JDY/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Jabra-Evolve2-Headset-Cancelling-USB/product-reviews/B086H56JDY/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Jabra-Evolve2-Headset-Cancelling-USB/product-reviews/B086H56JDY/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Jabra-Evolve2-Headset-Cancelling-USB/product-reviews/B086H56JDY/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review26 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review26)

```


#Product 27
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset27 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset27)
}

link1 <- "https://www.amazon.com.au/Poly-Wireless-Plantronics-Headphones-Bluetooth/product-reviews/B09BBSM3JL/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Poly-Wireless-Plantronics-Headphones-Bluetooth/product-reviews/B09BBSM3JL/ref=cm_cr_getr_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Poly-Wireless-Plantronics-Headphones-Bluetooth/product-reviews/B09BBSM3JL/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Poly-Wireless-Plantronics-Headphones-Bluetooth/product-reviews/B09BBSM3JL/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Poly-Wireless-Plantronics-Headphones-Bluetooth/product-reviews/B09BBSM3JL/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review27 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review27)

```


#Product 28
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset28 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset28)
}

link1 <- "https://www.amazon.com.au/Hollyland-Solidcom-Communication-Headphone-Microphone/product-reviews/B09V7VQFQN/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Hollyland-Solidcom-Communication-Headphone-Microphone/product-reviews/B09V7VQFQN/ref=cm_cr_getr_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Hollyland-Solidcom-Communication-Headphone-Microphone/product-reviews/B09V7VQFQN/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Hollyland-Solidcom-Communication-Headphone-Microphone/product-reviews/B09V7VQFQN/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Hollyland-Solidcom-Communication-Headphone-Microphone/product-reviews/B09V7VQFQN/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review28 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review28)

```


#Product 29
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset29 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset29)
}

link1 <- "https://www.amazon.com.au/SteelSeries-Arctis-Wired-Gaming-Headset/product-reviews/B07SJHG1MJ/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/SteelSeries-Arctis-Wired-Gaming-Headset/product-reviews/B07SJHG1MJ/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/SteelSeries-Arctis-Wired-Gaming-Headset/product-reviews/B07SJHG1MJ/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/SteelSeries-Arctis-Wired-Gaming-Headset/product-reviews/B07SJHG1MJ/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/SteelSeries-Arctis-Wired-Gaming-Headset/product-reviews/B07SJHG1MJ/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review29 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review29)
```


#Product 30
```{r}
category <- "Headset"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonheadset30 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonheadset30)
}

link1 <- "https://www.amazon.com.au/Turtle-Beach-Headset-Recon-70N/product-reviews/B07NH6Q4LB/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Turtle-Beach-Headset-Recon-70N/product-reviews/B07NH6Q4LB/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Turtle-Beach-Headset-Recon-70N/product-reviews/B07NH6Q4LB/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Turtle-Beach-Headset-Recon-70N/product-reviews/B07NH6Q4LB/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Turtle-Beach-Headset-Recon-70N/product-reviews/B07NH6Q4LB/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review30 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review30)
```


#Product 31
```{r}
category <- "Shoes"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonshoes1 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonshoes1)
}

link1 <- "https://www.amazon.com.au/Skechers-Womens-Uno-Lace-Up-Sneaker/product-reviews/B0CR97XY75/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Skechers-Womens-Uno-Lace-Up-Sneaker/product-reviews/B0CR97XY75/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Skechers-Womens-Uno-Lace-Up-Sneaker/product-reviews/B0CR97XY75/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Skechers-Womens-Uno-Lace-Up-Sneaker/product-reviews/B0CR97XY75/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Skechers-Womens-Uno-Lace-Up-Sneaker/product-reviews/B0CR97XY75/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review31 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review31)
```


#Product 32
```{r}
category <- "Shoes"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonshoes2 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonshoes2)
}

link1 <- "https://www.amazon.com.au/Tommy-Hilfiger-Essential-Leather-Sneaker/product-reviews/B0CJ8CD94N/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Tommy-Hilfiger-Essential-Leather-Sneaker/product-reviews/B0CJ8CD94N/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Tommy-Hilfiger-Essential-Leather-Sneaker/product-reviews/B0CJ8CD94N/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Tommy-Hilfiger-Essential-Leather-Sneaker/product-reviews/B0CJ8CD94N/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Tommy-Hilfiger-Essential-Leather-Sneaker/product-reviews/B0CJ8CD94N/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review32 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review32)
```


#Product 33
```{r}
category <- "Shoes"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonshoes3 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonshoes3)
}

link1 <- "https://www.amazon.com.au/PUMA-385849/product-reviews/B09L5VV6D6/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/PUMA-385849/product-reviews/B09L5VV6D6/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/PUMA-385849/product-reviews/B09L5VV6D6/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/PUMA-385849/product-reviews/B09L5VV6D6/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/PUMA-385849/product-reviews/B09L5VV6D6/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review33 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review33)
```


#Product 34
```{r}
category <- "Shoes"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonshoes4 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonshoes4)
}

link1 <- "https://www.amazon.com.au/GUESS-gwLOVEN4/product-reviews/B08H17RPY7/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/GUESS-gwLOVEN4/product-reviews/B08H17RPY7/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/GUESS-gwLOVEN4/product-reviews/B08H17RPY7/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/GUESS-gwLOVEN4/product-reviews/B08H17RPY7/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/GUESS-gwLOVEN4/product-reviews/B08H17RPY7/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review34 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review34)
```


#Product 35
```{r}
category <- "Shoes"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonshoes5 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonshoes5)
}

link1 <- "https://www.amazon.com.au/Crocs-Womens-Clock-Resistant-Shoes/product-reviews/B096MM7Q7J/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Crocs-Womens-Clock-Resistant-Shoes/product-reviews/B096MM7Q7J/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Crocs-Womens-Clock-Resistant-Shoes/product-reviews/B096MM7Q7J/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Crocs-Womens-Clock-Resistant-Shoes/product-reviews/B096MM7Q7J/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Crocs-Womens-Clock-Resistant-Shoes/product-reviews/B096MM7Q7J/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review35 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review35)
```


#Product 36
```{r}
category <- "Shoes"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonshoes6 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonshoes6)
}

link1 <- "https://www.amazon.com.au/Sloggers%C2%AE-5120BEEBL09-Waterproof-Comfort-Shoe/product-reviews/B07T1NVLH7/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Sloggers%C2%AE-5120BEEBL09-Waterproof-Comfort-Shoe/product-reviews/B07T1NVLH7/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Sloggers%C2%AE-5120BEEBL09-Waterproof-Comfort-Shoe/product-reviews/B07T1NVLH7/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Sloggers%C2%AE-5120BEEBL09-Waterproof-Comfort-Shoe/product-reviews/B07T1NVLH7/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Sloggers%C2%AE-5120BEEBL09-Waterproof-Comfort-Shoe/product-reviews/B07T1NVLH7/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review36 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review36)
```


#Product 37
```{r}
category <- "Shoes"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonshoes7 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonshoes7)
}

link1 <- "https://www.amazon.com.au/Salomon-Mens-Speedcross-Trail-Running/product-reviews/B0CSKFTGXQ/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Salomon-Mens-Speedcross-Trail-Running/product-reviews/B0CSKFTGXQ/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Salomon-Mens-Speedcross-Trail-Running/product-reviews/B0CSKFTGXQ/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Salomon-Mens-Speedcross-Trail-Running/product-reviews/B0CSKFTGXQ/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Salomon-Mens-Speedcross-Trail-Running/product-reviews/B0CSKFTGXQ/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review37 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review37)
```


#Product 38
```{r}
category <- "Shoes"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonshoes8 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonshoes8)
}

link1 <- "https://www.amazon.com.au/crocs-Mens-Santa-Cruz-Loafers/product-reviews/B079TXBCBX/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/crocs-Mens-Santa-Cruz-Loafers/product-reviews/B079TXBCBX/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/crocs-Mens-Santa-Cruz-Loafers/product-reviews/B079TXBCBX/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/crocs-Mens-Santa-Cruz-Loafers/product-reviews/B079TXBCBX/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/crocs-Mens-Santa-Cruz-Loafers/product-reviews/B079TXBCBX/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review38 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review38)
```


#Product 39
```{r}
category <- "Shoes"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonshoes9 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonshoes9)
}

link1 <- "https://www.amazon.com.au/Dr-Martens-Unisex-Lace-Up-Leather/product-reviews/B0CM3Z1M6L/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Dr-Martens-Unisex-Lace-Up-Leather/product-reviews/B0CM3Z1M6L/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Dr-Martens-Unisex-Lace-Up-Leather/product-reviews/B0CM3Z1M6L/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Dr-Martens-Unisex-Lace-Up-Leather/product-reviews/B0CM3Z1M6L/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Dr-Martens-Unisex-Lace-Up-Leather/product-reviews/B0CM3Z1M6L/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review39 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review39)
```


#Product 40
```{r}
category <- "Shoes"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonshoes10 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonshoes10)
}

link1 <- "https://www.amazon.com.au/Skechers-Work-Relaxed-Fit-Cessnock/product-reviews/B07MKB9JKY/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Skechers-Work-Relaxed-Fit-Cessnock/product-reviews/B07MKB9JKY/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Skechers-Work-Relaxed-Fit-Cessnock/product-reviews/B07MKB9JKY/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Skechers-Work-Relaxed-Fit-Cessnock/product-reviews/B07MKB9JKY/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Skechers-Work-Relaxed-Fit-Cessnock/product-reviews/B07MKB9JKY/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review40 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review40)
```


#Product 41
```{r}
category <- "Shoes"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonshoes11 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonshoes11)
}

link1 <- "https://www.amazon.com.au/Skechers/product-reviews/B0CSF3CP3Z/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Skechers/product-reviews/B0CSF3CP3Z/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Skechers/product-reviews/B0CSF3CP3Z/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Skechers/product-reviews/B0CSF3CP3Z/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Skechers/product-reviews/B0CSF3CP3Z/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review41 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review41)
```


#Product 42
```{r}
category <- "Shoes"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonshoes12 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonshoes12)
}

link1 <- "https://www.amazon.com.au/Columbia/product-reviews/B0CTHY8Z3X/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Columbia/product-reviews/B0CTHY8Z3X/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Columbia/product-reviews/B0CTHY8Z3X/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Columbia/product-reviews/B0CTHY8Z3X/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Columbia/product-reviews/B0CTHY8Z3X/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review42 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review42)
```


#Product 43
```{r}
category <- "Shoes"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonshoes13 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonshoes13)
}

link1 <- "https://www.amazon.com.au/MERRELL-J067663/product-reviews/B0BVXVG4MF/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/MERRELL-J067663/product-reviews/B0BVXVG4MF/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/MERRELL-J067663/product-reviews/B0BVXVG4MF/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/MERRELL-J067663/product-reviews/B0BVXVG4MF/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/MERRELL-J067663/product-reviews/B0BVXVG4MF/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review43 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review43)
```


#Product 44
```{r}
category <- "Shoes"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonshoes14 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonshoes14)
}

link1 <- "https://www.amazon.com.au/adidas-Performance-Runfalcon/product-reviews/B0CV869L18/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/adidas-Performance-Runfalcon/product-reviews/B0CV869L18/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/adidas-Performance-Runfalcon/product-reviews/B0CV869L18/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/adidas-Performance-Runfalcon/product-reviews/B0CV869L18/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/adidas-Performance-Runfalcon/product-reviews/B0CV869L18/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review44 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review44)
```


#Product 45
```{r}
category <- "Shoes"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonshoes15 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonshoes15)
}

link1 <- "https://www.amazon.com.au/DC-Shoes-108876/product-reviews/B0C9V71Z15/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/DC-Shoes-108876/product-reviews/B0C9V71Z15/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/DC-Shoes-108876/product-reviews/B0C9V71Z15/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/DC-Shoes-108876/product-reviews/B0C9V71Z15/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/DC-Shoes-108876/product-reviews/B0C9V71Z15/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review45 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review45)
```


#Product 46
```{r}
category <- "Shoes"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonshoes16 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonshoes16)
}

link1 <- "https://www.amazon.com.au/PUMA-Mens-Tazon-Cross-Training-Shoe/product-reviews/B0C5MZPMZD/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/PUMA-Mens-Tazon-Cross-Training-Shoe/product-reviews/B0C5MZPMZD/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/PUMA-Mens-Tazon-Cross-Training-Shoe/product-reviews/B0C5MZPMZD/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/PUMA-Mens-Tazon-Cross-Training-Shoe/product-reviews/B0C5MZPMZD/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/PUMA-Mens-Tazon-Cross-Training-Shoe/product-reviews/B0C5MZPMZD/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review46 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review46)
```


#Product 47
```{r}
category <- "Shoes"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonshoes17 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonshoes17)
}

link1 <- "https://www.amazon.com.au/etnies-Mens-Jameson-Skate-Medium/product-reviews/B0CN1LLZMR/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/etnies-Mens-Jameson-Skate-Medium/product-reviews/B0CN1LLZMR/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/etnies-Mens-Jameson-Skate-Medium/product-reviews/B0CN1LLZMR/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/etnies-Mens-Jameson-Skate-Medium/product-reviews/B0CN1LLZMR/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/etnies-Mens-Jameson-Skate-Medium/product-reviews/B0CN1LLZMR/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review47 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review47)
```


#Product 48
```{r}
category <- "Shoes"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonshoes18 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonshoes18)
}

link1 <- "https://www.amazon.com.au/Heelys/product-reviews/B0CWS2J393/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/Heelys/product-reviews/B0CWS2J393/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/Heelys/product-reviews/B0CWS2J393/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/Heelys/product-reviews/B0CWS2J393/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/Heelys/product-reviews/B0CWS2J393/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review48 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review48)
```


#Product 49
```{r}
category <- "Shoes"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonshoes19 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonshoes19)
}

link1 <- "https://www.amazon.com.au/ECCO-Mens-St1-Hybrid-Plain/product-reviews/B07FQ4SQLK/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/ECCO-Mens-St1-Hybrid-Plain/product-reviews/B07FQ4SQLK/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/ECCO-Mens-St1-Hybrid-Plain/product-reviews/B07FQ4SQLK/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/ECCO-Mens-St1-Hybrid-Plain/product-reviews/B07FQ4SQLK/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/ECCO-Mens-St1-Hybrid-Plain/product-reviews/B07FQ4SQLK/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review49 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review49)
```


#Product 50
```{r}
category <- "Shoes"
scrapeNodes <- function(session, HTML) {
  session %>% scrape() %>% html_nodes(HTML) %>% html_text()
}
productinfo <- function(link) {
  session <- bow(link, user_agent = "For Educational Purpose")
  Sys.sleep(5) 
        Product <- scrapeNodes(session, "h1.a-size-large.a-text-ellipsis")
  
        Product_Reviewer <- scrapeNodes(session, "span.a-profile-name")[1:10]
  
        Product_Review <- scrapeNodes(session, "span.a-size-base.review-text.review-text-content")[1:10]
        
         verified_reviews<-scrapeNodes(session, "span.a-size-mini.a-color-state.a-text-bold")[1:10]
  
        Review_Date <- scrapeNodes(session, "span.a-size-base.a-color-secondary.review-date")[1:10]
  
        Product_Ratings <- scrapeNodes(session, "span.a-icon-alt")[1:10]
  
  amazonshoes20 <- data.frame(Category = category,
                        ProductName = Product,
                        Reviewer = Product_Reviewer,
                        Review = Product_Review,
                        Verified = verified_reviews,
                        DateOfReview = Review_Date,
                        Rating = Product_Ratings)
  return(amazonshoes20)
}

link1 <- "https://www.amazon.com.au/DSC-Beamer-Cricket-Economical-Durable/product-reviews/B0BZKBYDSG/ref=cm_cr_dp_d_show_all_btm?ie=UTF8&reviewerType=all_reviews"
pg1 <- productinfo(link1)
link2 <- "https://www.amazon.com.au/DSC-Beamer-Cricket-Economical-Durable/product-reviews/B0BZKBYDSG/ref=cm_cr_arp_d_paging_btm_next_2?ie=UTF8&reviewerType=all_reviews&pageNumber=2"
pg2 <- productinfo(link2)
link3 <- "https://www.amazon.com.au/DSC-Beamer-Cricket-Economical-Durable/product-reviews/B0BZKBYDSG/ref=cm_cr_getr_d_paging_btm_next_3?ie=UTF8&reviewerType=all_reviews&pageNumber=3"
pg3 <- productinfo(link3)
link4 <- "https://www.amazon.com.au/DSC-Beamer-Cricket-Economical-Durable/product-reviews/B0BZKBYDSG/ref=cm_cr_getr_d_paging_btm_next_4?ie=UTF8&reviewerType=all_reviews&pageNumber=4"
pg4 <- productinfo(link4)
link5 <- "https://www.amazon.com.au/DSC-Beamer-Cricket-Economical-Durable/product-reviews/B0BZKBYDSG/ref=cm_cr_getr_d_paging_btm_next_5?ie=UTF8&reviewerType=all_reviews&pageNumber=5"
pg5 <- productinfo(link5)

product_review50 <- rbind(pg1, pg2, pg3, pg4, pg5)

#View(product_review50)
```

```{r}
product_reviews <- bind_rows(product_review1, product_review2, product_review3, product_review4, product_review5, product_review10, product_review11, product_review12, product_review13, product_review14, product_review15, product_review16, product_review17, product_review18, product_review19, product_review20, product_review21, product_review22, product_review23, product_review24, product_review25, product_review26, product_review27, product_review28, product_review29, product_review30, product_review31, product_review32, product_review33, product_review34, product_review35, product_review36, product_review37, product_review38, product_review39, product_review40, product_review41, product_review42, product_review43, product_review44, product_review45, product_review46, product_review47, product_review48, product_review49, product_review50)

write.csv(product_reviews, file = "50AmazonProducts_Reviews.csv")
```